A Formal Model of Checked C

### 2023-01-15 sandp23/appendix.tex
finished appx.

\subsubsection{parsons}
Parsons is annotated comprehensively in two variants parsons\_wasm and parsons\_tainted. parsons\_wasm has most of its input parsing functions moved into the sandbox, whilst having all its pointers marked as tainted. These sandboxed functions interact with the checked region by making indirect calls through RLBOX's callback mechanism. However, with parsons\_tainted, we do not move any of the functions to the sandbox but still mark all the pointers as tainted. The test suite itself consists of 328 tests comprehensively testing the JSON parser's functionality. Benchmarks for both of these forks are recorded using the mean difference between the \systemname and generic-C/checked-C variants when executing 10 consecutive iterations of the test suite. parsons\_wasm expectedly shows 200/266\% runtime overhead when evaluated against checked-c and generic-c respectively due to the performance limitation of WebAssembly. However, evaluating parsons\_tainted against checked-c shows \systemname to be faster because \systemname by itself performs lighter run-time-instrumentation on tainted pointers as compared to the run-time bounds checking performed on checked pointers by checked-c. Furthermore, we only see an average peak memory of 9.5 KiB as compared to the anticipated 82 KiB overhead as Valgrind does not consider the WASM Shadow memory allocated to the tainted pointers.

\subsubsection{LibPNG}
\systemname changes for libPNG is narrow in scope and begins with the encapsulation CVE-2018-144550 and a buffer overflow in compare\_read(). However, we also annotate sections of Lib-png that involve reading, writing, and image processing (interlace, intrapixel, etc) on user-input image data as tainted. That is, rows of image bytes are read into tainted pointers and the taintedness for the row\_bytes is propagated throughout the program. All our changes extend to the png2pnm and pnm2png executables. To evaluate png2pnm, we take the mean of 10 iterations of a test script that runs png2pnm on 52 png files located within the libpng's pngsuite. To test pnm2png, we take the mean of 10 iterations of pnm2png in converting a 52MB 5184x3456 pixels large pnm image file to png. Valgrind's reported lower Heap space consumption for \systemname converted code is due to the discounted space consumed on the heap by the Sandbox's shadow memory. Consequently, when evaluating pnm2png, \systemname's heap consumption was 52 MB lower as the entire image was loaded onto the shadow memory.

\subsubsection{MicroHTTPD}
MicroHTTPD demonstrates the practical difficulties in converting a program to \systemname. Our conversion for this program was aimed at sandboxing memory vulnerabilities CVE-2021-3466 and CVE-2013-7039. CVE-2021-3466 is described as a vulnerability from a buffer overflow that occurs in an unguarded "memcpy" which copies data into a structure pointer (struct MHD\_PostProcessor pp) which is type-casted to a char buffer (char *kbuf = (char *) \&pp[1]). Our changes would require making the "memcpy" safe by marking this pointer as tainted. However, this would either require marshaling the data pointed by this structure (and its sub-structure pointer members) pointer or would require marking every reference to this structure pointer as tainted, which in turn requires every pointer member of this structure to be tainted. Marshalling data between structure pointers is not easy and demands substantial marshaling code due to the spatial non-linearity of its pointer members unlike a char*. This did not align with our conversion goals which were aimed at making minimal changes. Consequently, the above CVE stands un-handled by \systemname.  Our changes for CVE-2013-7039 involve marking the user input data arguments of this function as tainted pointers and in the interests of seeking minimal conversion changes, we do not propagate the tainted-ness on these functions. Following up on the chronological impossibility of sandboxing bugs before they are discovered and the general programmer intuiting, we moved many of the core internal functions (like MHD\_str\_pct\_decode\_strict\_() and MHD\_http\_unescape()) into the sandbox.

\subsubsection{Tiny-bignum}
Due to its small size and simplicity, \systemname changes for Tiny-bignum was chosen to be comprehensive. Furthermore, bignum\_to\_string() was moved to the sandbox due to a memory-unsafe use of sprintf(). Given that significant \systemname conversion efforts is attributed to understanding the source-code and finding the precise extent to which we choose to propagate the taintedness or to stop and give up to marshalling the data between regions, Tiny-bignum only required 4 hours. The evaluation was performed on Tiny-bignum's test suite consisting of 4 Test cases, each of which test the functionality to scale on big numbers subject to all of the supported unary and binary operations.

>>>>

Here, we provide the description of additional program evaluations.

\myparagraph{parsons}
Parsons is annotated comprehensively in two variants parsons\_wasm and parsons\_tainted. parsons\_wasm has most of its input parsing functions moved into the sandbox, whilst having all its pointers marked as tainted. These sandboxed functions interact with the checked region by making indirect calls through RLBOX's callback mechanism. However, with parsons\_tainted, we do not move any of the functions to the sandbox but still mark all the pointers as tainted. The test suite itself consists of 328 tests comprehensively testing the JSON parser's functionality. Benchmarks for both of these forks are recorded using the mean difference between the \systemname and generic-C/checked-C variants when executing 10 consecutive iterations of the test suite. parsons\_wasm expectedly shows 200/266\% runtime overhead when evaluated against checked-c and generic-c respectively due to the performance limitation of WebAssembly. However, evaluating parsons\_tainted against checked-c shows \systemname to be faster because \systemname by itself performs lighter run-time-instrumentation on tainted pointers as compared to the run-time bounds checking performed on checked pointers by checked-c. Furthermore, we only see an average peak memory of 9.5 KiB as compared to the anticipated 82 KiB overhead as Valgrind does not consider the WASM Shadow memory allocated to the tainted pointers.

\myparagraph{LibPNG}
\systemname changes for libPNG is narrow in scope and begins with the encapsulation CVE-2018-144550 and a buffer overflow in compare\_read(). However, we also annotate sections of Lib-png that involve reading, writing, and image processing (interlace, intrapixel, etc) on user-input image data as tainted. That is, rows of image bytes are read into tainted pointers and the taintedness for the row\_bytes is propagated throughout the program. All our changes extend to the png2pnm and pnm2png executables. To evaluate png2pnm, we take the mean of 10 iterations of a test script that runs png2pnm on 52 png files located within the libpng's pngsuite. To test pnm2png, we take the mean of 10 iterations of pnm2png in converting a 52MB 5184x3456 pixels large pnm image file to png. Valgrind's reported lower Heap space consumption for \systemname converted code is due to the discounted space consumed on the heap by the Sandbox's shadow memory. Consequently, when evaluating pnm2png, \systemname's heap consumption was 52 MB lower as the entire image was loaded onto the shadow memory.

\myparagraph{MicroHTTPD}
MicroHTTPD demonstrates the practical difficulties in converting a program to \systemname. Our conversion for this program was aimed at sandboxing memory vulnerabilities CVE-2021-3466 and CVE-2013-7039. CVE-2021-3466 is described as a vulnerability from a buffer overflow that occurs in an unguarded "memcpy" which copies data into a structure pointer (struct MHD\_PostProcessor pp) which is type-casted to a char buffer (char *kbuf = (char *) \&pp[1]). Our changes would require making the "memcpy" safe by marking this pointer as tainted. However, this would either require marshaling the data pointed by this structure (and its sub-structure pointer members) pointer or would require marking every reference to this structure pointer as tainted, which in turn requires every pointer member of this structure to be tainted. Marshalling data between structure pointers is not easy and demands substantial marshaling code due to the spatial non-linearity of its pointer members unlike a char*. This did not align with our conversion goals which were aimed at making minimal changes. Consequently, the above CVE stands un-handled by \systemname.  Our changes for CVE-2013-7039 involve marking the user input data arguments of this function as tainted pointers and in the interests of seeking minimal conversion changes, we do not propagate the tainted-ness on these functions. Following up on the chronological impossibility of sandboxing bugs before they are discovered and the general programmer intuiting, we moved many of the core internal functions (like MHD\_str\_pct\_decode\_strict\_() and MHD\_http\_unescape()) into the sandbox.

\myparagraph{Tiny-bignum}
Due to its small size and simplicity, \systemname changes for Tiny-bignum was chosen to be comprehensive. Furthermore, bignum\_to\_string() was moved to the sandbox due to a memory-unsafe use of sprintf(). Given that significant \systemname conversion efforts is attributed to understanding the source-code and finding the precise extent to which we choose to propagate the taintedness or to stop and give up to marshalling the data between regions, Tiny-bignum only required 4 hours. The evaluation was performed on Tiny-bignum's test suite consisting of 4 Test cases, each of which test the functionality to scale on big numbers subject to all of the supported unary and binary operations.
